\textls[-0]{\thetitle}

### 2023-03-17 coqimpl.tex
tweak

The \Lang implementation currently does not support the full set of the Coq
facility for inductive types and fixpoints;
in particular, mutually inductive types and mutual fixpoints are not supported.
The plugin supports indexed inductive types but not parameterized ones, though
the latter can be encoded via the former.
Partial recursors are automatically generated only for non-indexed inductive types.
We believe that these limitations do not pose conceptual challenges and can be
addressed with more engineering effort of the same kind that went into \Lang.

@@

However, there are also limitations we believe require more research effort, including but not limited to: 
\begin{itemize}
  \item We didn't considered the compatibility of universe polymorphism mechanism of Coq with our plugin except we know our plugin elaborate families into modules. Thus our implementation is supposed to be as compatible with universe polymorphism as Coq's Module.\YZ{Is this really a limitation at all? Do we have to mention it?}
  \item ... \YZ{mention restricting induction to the top level}
  \item We don't support normalization of the open term using extensible inductive type. When applying recursor $Rec$ to open terms $t$ using extensible inductive type, the computation cannot be done by the Coq's kernel, thus the computation result of $Rec(t)$ is only propositionally equal (but not judgementally equal) to $Rec(t)$. It will complicate typechecking of the dependently typed terms. 
\end{itemize}

>>>>

The \Lang implementation currently does not support Coq's full
facility for inductive types and fixpoints;
in particular, mutually inductive types and mutual fixpoints are not supported.
The plugin supports indexed inductive types but not parameterized ones, though
the latter can be encoded via the former.
Partial recursors are automatically generated only for non-indexed inductive types.
We believe that these limitations do not pose conceptual challenges and can be
addressed with more engineering effort of the same kind that went into \Lang.

@@

However, there are also limitations we believe require more research effort or more thought from a language-design perspective, including but not limited to: 
\begin{itemize}
  \item We didn't considered the compatibility of universe polymorphism mechanism of Coq with our plugin except we know our plugin elaborate families into modules. Thus our implementation is supposed to be as compatible with universe polymorphism as Coq's Module.\YZ{Is this really a limitation at all? Do we have to mention it?}
  \item ... \YZ{mention restricting induction to the top level}
  \item We don't support normalization of the open term using extensible inductive type. When applying recursor $Rec$ to open terms $t$ using extensible inductive type, the computation cannot be done by the Coq's kernel, thus the computation result of $Rec(t)$ is only propositionally equal (but not judgementally equal) to $Rec(t)$. It will complicate typechecking of the dependently typed terms. 
\end{itemize}
